D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-04-07 doc/proposal/proposal.tex
Proposal edit

\title{D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling}
\author{Napolitano Saverio, Ricciardi Nicola, Garagnani Filippo}
\date{\today}

\pagestyle{fancy}
\fancyhead[L]{D.I.A.G.R.A.M. Proposal}
\fancyhead[R]{Napolitano, Ricciardi, Garagnani}

@@

\section{Introduction}
    Diagrams are a powerful means of representing complex systems, ideas, and relationships. Writing diagrams in code format is extremely efficient to easily edit the diagram and to display it in a better-formed format. This project aims to automate the conversion of handwritten diagrams into code, streamlining the process of diagram creation and visualization.

@@

\section{System Architecture}
    The project will be composed of different modules that will be stacked together in an uniform pipeline [see Figure 1]. These components are:
    \begin{itemize}
    		\item \textbf{Preprocessor}: Applies some operations (like denoising, rotation...) in order to obtain a more suitable input image for the following modules.
    		\item \textbf{Classifier}: In order to manage more than one type of diagrams, a classifier that identifies the category of the input diagram is needed.
    		\item \textbf{Extractor}: By employing feature extraction, image segmentation and static analysis over the recognized components, the extractor will output a robust structure to contain all the relevant information about the diagram. This key component takes the image as input and will output the entities found, their relations and more useful information.
    		\item \textbf{Transducer}: From the data output by the extractor, a certain transducer will give out a formatted code relative to the input diagram. We envision a single transducer for every supported language.
    		\item \textbf{Compiler}: Given the code, the compiler will convert it into an output image - hopefully, as close as possible as the input diagram.
    \end{itemize}

@@

>>>>

\renewcommand{\abstractname}{Summary}

\title{D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling}
\author{Filippo Garagnani, Saverio Napolitano, Nicola Ricciardi}
\date{\today}

\pagestyle{fancy}
\fancyhead[L]{D.I.A.G.R.A.M. - Project Proposal}
\fancyhead[R]{\small Garagnani, Napolitano, Ricciardi}

@@

\section{Introduction}
    Diagrams are a powerful means of representing complex systems, ideas, and relationships. Writing diagrams in a textual format is extremely efficient to easily edit the diagram and to display it in a better-formed format. This project aims to automate the conversion of handwritten diagrams into code, streamlining the process of diagram creation and visualization.

@@

\section{System Architecture}
    The project will be composed of different modules that will be stacked together in an uniform pipeline [\textbf{Figure 1}]. These components are:
    \begin{itemize}
    		\item \textbf{Preprocessor}: Applies some operations (like denoising, rotation...) in order to obtain a more suitable input image for the following modules.
    		\item \textbf{Classifier}: In order to manage more than one type of diagrams, a classifier that identifies the category of the input diagram is needed.
    		\item \textbf{Extractor}: By employing feature extraction, image segmentation and static analysis over the recognized components, the extractor will output a robust structure to contain all the relevant information about the diagram. This key component takes the image as input and will output the entities found, their relations and more useful information.
    		\item \textbf{Transducer}: From the data output by the extractor, a certain transducer will give out a formatted code relative to the input diagram. We envision a single transducer for every supported language.
    		\item \textbf{Compiler}: Given the code, the compiler will convert it into an output image - hopefully, as close as possible as the input diagram.
    \end{itemize}

@@

\newpage

\section{Constraint}
While the whole project idea could be applied to a wide variety of diagrams and languages, in order to manage the complexity we decided to impose a few theoretical constraints:

	\begin{enumerate}

	\item \textbf{Types of diagrams}: We restrict the types of diagrams that the system is able to correctly recognize and reconstruct (\textit{e.g.} Graph diagrams, Flowchart diagrams...)
	\item \textbf{Languages}: Even if there are various languages in which the diagrams could be formatted, we limit the languages that the system could translate the diagrams to (\textit{e.g.} Mermaid, D2...)

	\end{enumerate}
